05_DESeq_manipulation

### 2019-05-20 analysis/05_DESeq2_manipulate.Rmd
now with grids

```{r totalDEGs, eval = F}
#create list of groups for deseq contrasts
group1 <- c("m.inc.d3","m.inc.d8", "m.inc.d9", "m.inc.d17", "prolong","extend", "m.n2" ) 
group2 <- group1

@@

>>>>

```{r totalDEGs, eval = T}
#create list of groups for deseq contrasts
group1 <- c("m.inc.d3","m.inc.d8", "m.inc.d9", "m.inc.d17", "prolong","extend", "m.n2" ) 
group2 <- group1

@@

```{r totalDEGs2}
plot_grid(a + theme_minimal(base_size = 8) + theme(legend.position = "none", axis.text.x = element_text(angle = 90)),
          b + theme_minimal(base_size = 8) + theme(legend.position = "none", axis.text.x = element_text(angle = 90)),
          c + theme_minimal(base_size = 8) + theme(axis.text.x = element_text(angle = 90)),
          d + theme_minimal(base_size = 8) + theme(legend.position = "none",axis.text.x = element_text(angle = 90)),
          e + theme_minimal(base_size = 8) + theme(legend.position = "none",axis.text.x = element_text(angle = 90)),
          f + theme_minimal(base_size = 8) + theme(axis.text.x = element_text(angle = 90)),
          nrow = 2, rel_widths = c(0.3, 0.3, 0.4)) 
```
